---
name: Andrés Castro Araújo
position: "Social Scientist, Statistician"
address: "New York, NY"
phone: +1 718 360-6862
email: "acastroaraujo@gmail.com, andres.castro@columbia.edu"
github: acastroaraujo
output: vitae::twentyseconds
aboutme: "`r readLines('custom_text.txt')`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
```

# Experience

\vspace{0.3cm}

**RESEARCHER | 2015 - 2017** \newline 
**Center for Law, Justice, and Society - Dejusticia**

The YAML header contains general entries that are common across many templates, such as your name, address and social media profiles. This is also where the output format (the CV template used) is specified, along with any options that the template supports. An example of what this header may look like is shown below:

**ADJUNCT LECTURER | 2016 - 2017** \newline
**University of Rosario, School of Human Sciences**

- I poisoned myself doing research.
- I was the first woman to win a Nobel prize

    + I was the first person and only woman to win a Nobel prize in two different sciences.
    
    + I was the first person and only woman to win a Nobel prize in two different sciences.
    
$$
\int f(x)dx
$$
    
## $1990-2018$

$Latex$

The YAML header contains general entries that are common across many templates, such as your name, address and social media profiles. This is also where the output format (the CV template used) is specified, along with any options that the template supports. An example of what this header may look like is shown below:


\vspace{0.3cm}
# Projects
\vspace{0.3cm}


## Twitter


The YAML header contains general entries that are common across many templates, such as your name, address and social media profiles. This is also where the output format (the CV template used) is specified, along with any options that the template supports. An example of what this header may look like is shown below:

```{r}
tibble::tribble(
  ~name, ~event, ~location, ~year,
  "Empowering people with community, software, and peer review",
  "**RUCK: R Users Conference Korea (Invited Keynote speaker)**",
  "Seoul, Korea", "2015 - 2018", 
  "Now you see it?  Now you don’t?  The role of graphics in identifying MCMC convergence (Awarded Runner up Pitman Prize for Young Statistician)", "ISCB-ASC", "Melbourne, Australia", 2018,
  "Find the best locations for facilities using `maxcovr`", "UseR! 2018", "Brisbane, Australia", 2018
) %>% 
  detailed_entries(
    what = name,
    when = year,
    with = event,
    where = location
  )
```


## Tax Havens


The YAML header contains general entries that are common across many templates, such as your name, address and social media profiles. This is also where the output format (the CV template used) is specified, along with any options that the template supports. An example of what this header may look like is shown below:


# Other

- Pasaporte a la Ciencia (Scholarship)

